%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ragged2e}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/dimasws/}{\Large Dimas Wahyu Saputro}} & Email : \href{mailto:dim.mas.ws@gmail.com}{dim.mas.ws@gmail.com}\\
  \href{https://www.linkedin.com/in/dimasws/}{https://linkedin.com/in/dimasws/} & Mobile : +62-851-5600-5717 \\
\end{tabular*}


%-----------About-----------------
\section{About}
    \justifying
    \textnormal{As an aspiring data scientist with a strong foundation in data visualization, stats, and programming, I am passionate about connecting the dots and using my technical abilities to solve complicated problems. I have experience in data wrangling, sampling, and experimental design, which has allowed me to make informed decisions in various industries. My expertise also includes applying AI and ML techniques to analyze and interpret data, leading to informed decision-making. I am excited to bring my skills and passions to new challenges and contribute to the prospective outlets for future contribution}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sumatera Institute of Technology}{Lampung Selatan, ID}
      {Bachelor of Science in Data Science;  GPA: 3.73}{Sep. 2020 -- Now}
    \resumeSubheading
      {Pacmann Academy}{Jakarta, ID}
      {Statistics - Data Talent Scholarship Awardee}{Dec 2022 - Jun 2023}
       \resumeItemListStart
         \resumeSubItem{Awardee Scholarship}
           {Out of 230++ applicants, I was chosen as one of the 35 awardee of the Pacmann Data and Business Talent Scholarship Batch 2.}
         \resumeSubItem{Module}
           {A comprehensive and intensive six-month course on Introduction to Data and Visualization was completed, where various skills including probability, Python, data wrangling, SQL, sampling, and experimental design were learned. More than 12 hours per week were dedicated to interactive classes, and practical experience was gained through the creation of over 10 data and business portfolios. This course equipped me with the necessary knowledge and skills to excel in a data-driven career.}
      %   \resumeSubItem{Conversational English Skills}
      %     {Learned conversational English skills for Business and Software Engineering on the Cakap platform, soft skills, and career readiness skills as a tech talent}
       \resumeItemListEnd
    \resumeSubheading
      {Generasi Gigih by YABB and GoTo}{Jakarta, ID}
      {Data Analyst Track}{Jan 2022 - Jul 2022}
      \resumeItemListStart
        \resumeSubItem{SQL and Python}
          {Self-paced completed SQL and Python courses on the Progate Platform}
        \resumeSubItem{Data Analyst Technical Skills}
          {Completed 52+ hours of data analyst technical skills such as Business Understanding, Statistical Methods, Data Management, SQL GCP BigQuery, Python, Google Data Studio Visualization, etc}
        \resumeSubItem{Conversational English Skills}
          {Learned conversational English skills for Business and Software Engineering on the Cakap platform, soft skills, and career readiness skills as a tech talent}
      \resumeItemListEnd
    % \resumeSubheading
    %  {Kredensial Mikro Mahasiswa Indonesia at ITS Surabaya}{Surabaya, ID}
    %  {Microsoft Azure Data and AI}{Aug 2021 - Oct 2021}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
    \resumeSubheading
      {Pacmann Academy}{Jakarta, ID}
      {Brand Ambassador}{Dec 2022 - Jun 2023}
    \resumeSubheading
      {Sumatera Institute of Technology}{Lampung Selatan, ID}
      {Practicum Assistant of Programming Algorithms}{Aug 2022 - Dec 2022}
      \resumeItemListStart
        \resumeItem{Tutored, Assist, Evaluate}
          {Tutored 40+ students of Basic Programming Algorithm with Python at weekly mentor session, assist students during laboratory section, and evaluate each student's assesment every week.}
      \resumeItemListEnd
    \resumeSubSubheading
     {Assistant Lecturer for Google Data Studio Visualization Workshop at PLN}{Oct 2022}
     \resumeItemListStart
        \resumeItem{Assist}
          {Assisted a group of over 20 PLN employees from various divisions in gaining proficiency in Google Data Studio. Led educational sessions and provided one-on-one guidance to ensure a thorough understanding of the platform and its potential for data visualization and analysis. Contributed to the improvement of data literacy within the organization.}
     \resumeItemListEnd
    \resumeSubSubheading
     {Head of Academic and Professional Departement - Himpunan Mahasiswa Sains Data}{Jan 2022 - Dec 2022}
    \resumeItemListStart
     \resumeItemListEnd
    \resumeSubSubheading
     {Assistant Lecturer for Basic Mathematics}{Jul 2021 - Dec 2021}
     \resumeItemListStart
        \resumeItem{Tutored, Assist, Evaluate}
          {Provided comprehensive guidance to TPB (Tahap Persiapan Bersama) students in the field of mathematics for engineering, covering both basic and advanced concepts. Assisted students in overcoming challenges and frustrations related to math problems, leveraging expertise in Calculus, Linear Algebra, and Statistics to facilitate successful application of mathematical principles in engineering. Contributed to the improvement of mathematical skills and confidence among TPB students.}
     \resumeItemListEnd
    % \resumeSubheading
    %  {Himpunan Mahasiswa Sains Data}{Lampung Selatan, ID}
    %  {Head of Academic and Professional Departement}{Jan 2022 - Now}
    % \resumeSubheading
    %   {Sumatera Institute of Technology}{Lampung Selatan, ID}
    %   {Teaching Assistant - Basic Mathematics }{Jul 2021 - Dec 2021}
    %   \resumeItemListStart
    %     \resumeSubItem{Assist}
    %       {Assist the teacher in organizing the learning environment, preparing and maintaining materials and resources, and grading tests and homework}
    %     \resumeSubItem{Support}
    %       {Support the teacher in execution of lesson plans, providing individual attention to student(s) during individual and group sessions}
    %     \resumeSubItem{Verify}
    %       {Verify and track attendance of students, observe student performance, contribute to reports, and maintain records as required}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{Time Series Analysis - SARIMA}
%       {Using SARIMA to Predict Numbers Train Passengers on Java Island}
%     \resumeSubItem{Firefly Algorithm - TSP}
%       {Firefly Algorithm Application for Troubleshooting Traveling Salesman Problem: Sumatra Institute of Technology Campus Building}
%    \resumeSubItem{Automated Form Filling}
%      {A project that was started because there were so many questionnaires that had to be filled out at the end of the semester, I created a feature to automatically fill out the questionnaire using Selenium.}
%    \resumeSubItem{Paid Promote Automate}
%      {When I first joined a student organization, I was surprised that there was such a thing as Paid Promote to get money. I'm overwhelmed. Therefore, I created a project that can automatically retrieve paid promote data from Telegram or the Website, then automatically upload it to Instagram.}
%  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{Go, Java, LaTeX, Python, R, SQL}
    \resumeSubItem{Technologies}{Docker, Git, Google BigQuery, Google Data Studio, Tableau}
  \resumeSubHeadingListEnd

%-------------------------------------------

\end{document}
